\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}

\usepackage{fontawesome}
\usepackage[a4paper, total={6.8in, 9.75in}]{geometry}
\usepackage{graphicx}

\usepackage[T1]{fontenc}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}

\input{glyphtounicode}

\setlength{\footskip}{5pt}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\columnSubheading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.45\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItemizeListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeItemizeListEnd}{\vspace{-5pt}\end{itemize}}

\newcommand{\resumeColumnStart}{\begin{multicols}{2}}
\newcommand{\resumeColumnEnd}{\end{multicols}}
%-------------------------------------------------------
%%%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Lakshya Jain} \\ \vspace{5pt}
    Junior Data-Centric Computing Student \\ \vspace{7pt}
    \small \href{tel:+15406050261}{\faPhone\ \underline{+1 (540) 605-0261}} $|$ 
    \href{mailto:lakshyajain@vt.edu}{\faEnvelope\ \underline{lakshyajain@vt.edu}} $|$ 
    \href{https://linkedin.com/in/lakshya46jain}{\faLinkedinSquare\ \underline{linkedin.com/in/lakshya46jain}} $|$ 
    \href{https://github.com/lakshya46jain}{\faGithub\ \underline{github.com/lakshya46jain}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Virginia Polytechnic Institute and State University (Virginia Tech)}{Blacksburg, VA}
      {B.S. Computer Science - Data-Centric Computing Major}{Expected Graduation: May 2026}
      \resumeItemizeListStart
        \small{\item{
        \textbf{Overall GPA}{: 3.16/4.00} | \textbf{Major GPA}{: 4.00/4.00} \\
        \textbf{Dean's List}{: Spring 2024} \\
        \textbf{Relevant Courses}{: Software Design, Data Structures \& Algorithms, Computer Organization \& Architecture} \\
        }}
      \resumeItemizeListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \resumeItemizeListStart
    \small{\item{
     \textbf{Languages}{: Java, Dart, Python, Swift, C, Assembly, R, JavaScript, TypeScript, MATLAB, HTML/CSS} \\
     \textbf{Front-end Frameworks}{: Flutter, React.js, Next.js, Material-UI, BootStrap} \\
     \textbf{Back-end Technologies}{: Firebase, PostgreSQL, SQL, Node.js, Express, REST APIs} \\
     \textbf{Cloud Technologies}{: Microsoft Azure (Machine Learning Studio), Google Cloud Platform (GCP)} \\
     \textbf{Data Science \& Machine Learning}{: NumPy, Pandas, TensorFlow, Keras, OpenCV} \\
     \textbf{Other}{: Docker, Git, GitHub, CI/CD (JUnit, PyTest), Visual Studio Code, Atom, Eclipse, Figma, Adobe XD, SolidWorks} \\
    }}
 \resumeItemizeListEnd

%-----------EXPERIENCE-----------
\section{Experience}

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------------

  \resumeSubHeadingListStart  
    \resumeSubheading
      {Undergraduate Grading Assistant}{Sep 2024 -- Present}
      {Virginia Tech College of Engineering}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{GA for ENGE 1215/1216: Foundations of Engineering (covers Core Engineering Concepts, MATLAB, SolidWorks).}
        \resumeItem{Assessed assignments for 140+ students, providing detailed feedback to enhance understanding of coursework.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research Assistant}{Sep 2024 -- Present}
      {Virginia Tech Department of Computer Science -- PASTA Lab}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{Collaborating on the development of an educational game focused on teaching children about privacy and security.}
        \resumeItem{Conducting research on gamification techniques to improve cybersecurity awareness amongst children.}
      \resumeItemListEnd

    \resumeSubheading
      {Virginia Tech Tutor}{Apr 2024 -- Present}
      {Knack -- Virginia Tech Student Success Center}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{Tutoring students in CS 2114 (Software Design and Data Structures - Java), earning a 5-star tutor rating.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Software Developer}{Jun 2023 -- Aug 2023}
      {Upgrid Creative}{Remote}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of 4 to develop cross-platform mobile app front-end using the Flutter framework.}
        \resumeItem{Redesigned the user interface (UI) for a restaurant application, improving usability and visual appeal.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Real Estate Analyzer} $|$ \emph{React.js, Python (Pandas), PostgreSQL, Azure, REST API, Places API}} {Sep 2024}
        \resumeItemListStart
         \resumeItem{Built a predictive web app estimating real estate prices with 97.5\% accuracy ($R^2$ = 0.9747) using Boosted Decision Tree Regression, achieving MAE of \$87,910 and RMSE of \$181,792.}
         \resumeItem{Trained and deployed a machine learning model on 428,000+ entries from the top 10 cities, each with top 10 zip codes based on data coverage in dataset,  across 45+ U.S. states using Microsoft Azure Machine Learning Studio.}
         \resumeItem{Delivered a fully functional prototype within 72 hours during VTHacks 12 by developing a scalable front-end with React.js and PostgreSQL for data logging.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Ticket Automation System} $|$ \emph{AppSheet, Google Sheets, Google Forms, Apps Script}} {Oct 2023 -- Nov 2023}
        \resumeItemListStart
         \resumeItem{Developed a mobile app integration between Google Sheets and AppSheet to automate the event ticketing process.}
         \resumeItem{Enabled real-time data access from Google Sheets and Forms, along with ticket scanning capabilities.}
         \resumeItem{Streamlined check-in for 400+ attendees for the Indian Students Association at Virginia Tech Diwali.}
        \resumeItemListEnd
    
      \resumeProjectHeading
        {\textbf{Help4You -- Cross-Platform Service Connector} $|$ \emph{Flutter, Firebase, OneSignal, REST API}}{Aug 2021 -- Jul 2023}
        \resumeItemListStart
         \resumeItem{Designed and developed a user-centric mobile app using Flutter, improving user experience across devices.}
         \resumeItem{Set up Firebase back-end (Authentication + Firestore + Cloud Storage) to store and query user-data and user-generated content, and optimized expensive write operations by using document references.}
         \resumeItem{Implemented live consumer-to-provider chat, enabling real-time communication and media sharing within the app.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------LEADERSHIP EXPERIENCE-----------
\section{Leadership Experience}

  \resumeSubHeadingListStart
    \resumeSubheading
      {President}{May 2024 -- Present}
      {Indian Students Association at Virginia Tech}{Blacksburg, VA}
      \resumeItemListStart
        \resumeItem{Leading a 30-student team to organize high-quality events for 500+ attendees, securing \$9,000+ in funding.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}